%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Consulting Member of Technical Staff} % Job title
    {Oracle Cloud Infrastructure} % Organization
    {Seattle} % Location
    {Feb. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, Implemented and Automated Backbone for OCI. Platforms involved Juniper Mx-480, Mx-10003 and Protocols involved IS-IS, MACSEC, RSVP-TE, TE++, BGP.}
        \item {Responsible for the path selection for all the new backbone routes, including SRLG and Capacity modelling. This involved Cariden MATE for WAN modeling and geo-spatial analysis for SRLG's from KMZ's.}
        \item {Introduced 100G platform and design for the Backbone and led the initial migration.}
        \item {Analysed and deployed various Forecasting Models for different areas of the Network. This involved primarily econometric models like ARIMA, ETS, TBATS etc.}
        \item {Time Series Analysis to understand Traffic patterns on how various parts of the network behaved.}
        \item {Build Data and CICD pipeline for Capacity Planning.}
        \item {Analysed and implemented Machine learning(ML) algorithms for gaining insights from the Network}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Solutions Architect} % Job title
    {Cisco Systems} % Organization
    {Bentonville, AR} % Location
    {Sep. 2015 - Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and deployed greenfield Backbone with Segment Routing. This was one of the very first SR deployment}
        \item {Led the design for EVPN with Vxlan for Datacenter fabric.}
        \item {Responsible for deep diving and driving operational readiness for new standards .Led a team of 3 NCE's}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Engineer} % Job title
    {Microsoft} % Organization
    {Redmond, WA} % Location
    {May. 2014 - July 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for design and maintenance of global IP/MPLS VPNs footprint.}
        \item {Focused on forward looking architecture and engineering design for various Microsoft Properties including Routing designs,peering,capacity management.}
        \item {Identified Telemetry coverage gaps and collaborated with various teams to fill the gaps. Identified gaps, brainstormed new ideas and improved the design process. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Engineer} % Job title
    {Dish Network} % Organization
    {Denver, Colorado} % Location
    {July. 2013 - April. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provide cross-domain architectural support in multiple technology areas including: system design, Routing, Security and provisioning services. }
        \item { Research and development in multiple technology areas, identifying long-term problems and technology solutions and architectures including routing (BGP, ISIS, MPLS, MPLS L3VPN’s, multicast), switching, and QoS policies.}
        \item {Lead Architect on internet Edge redesign, IPv6 deployment and network advancement for next generation network service framework.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Solutions Architect} % Job title
    {Cisco Systems} % Organization
    {Denver, Colorado} % Location
    {Feb. 2013 - June. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Maintain position as a subject matter expert in multiple technology areas. Provided consulting services to various customers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Network Engineer} % Job title
    {MSN Communications} % Organization
    {Denver, Colorado} % Location
    {Aug 2012 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Assessing Customer networks and architecting and designing a next-generation network and security architecture.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network Consulting Engineer} % Job title
    {Cisco Systems} % Organization
    {Raleigh NC} % Location
    {Jan 2008 - July. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designing customer’s network designs, providing technical expertise and consultation, and acting as a subject matter expert in multiple network technologies.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
